OTCE: Hybrid SSM and Attention with Cross Domain Mixture of Experts to construct Observer-Thinker-Conceiver-Expresser

### 2025-01-16 paper.tex
fist check
11

@@

In the precursor state space models of selective state space models, there are 4 parameters$(\Delta t, A, B, C)$, and they do not change with the input. These parameters control the following two stages:

% Note use of \abovespace and \belowspace to get reasonable spacing
% above and below tabular lines.

\begin{table}[t]
\caption{Classification accuracies for naive Bayes and flexible
Bayes on various data sets.}
\label{sample-table}
\vskip 0.15in
\begin{center}
\begin{small}
\begin{sc}
\begin{tabular}{lcccr}
\toprule
Data set & Naive & Flexible & Better? \\
\midrule
Breast    & 95.9$\pm$ 0.2& 96.7$\pm$ 0.2& $\surd$ \\
Cleveland & 83.3$\pm$ 0.6& 80.0$\pm$ 0.6& $\times$\\
Glass2    & 61.9$\pm$ 1.4& 83.8$\pm$ 0.7& $\surd$ \\
Credit    & 74.8$\pm$ 0.5& 78.3$\pm$ 0.6&         \\
Horse     & 73.3$\pm$ 0.9& 69.7$\pm$ 1.0& $\times$\\
Meta      & 67.1$\pm$ 0.6& 76.5$\pm$ 0.5& $\surd$ \\
Pima      & 75.1$\pm$ 0.6& 73.9$\pm$ 0.5&         \\
Vehicle   & 44.9$\pm$ 0.6& 61.5$\pm$ 0.4& $\surd$ \\
\bottomrule
\end{tabular}
\end{sc}
\end{small}
\end{center}
\vskip -0.1in
\end{table}

Tables contain textual material, whereas figures contain graphical material.
Specify the contents of each row and column in the table's topmost
row. Again, you may float tables to a column's top or bottom, and set
wide tables across both columns. Place two-column tables at the
top or bottom of the page.

>>>>

\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{xcolor}
\usepackage{booktabs}

@@

In the precursor state space models of selective state space models, there are 4 parameters$(\Delta t, A, B, C)$, and they do not change with the input. These parameters control the following two stages:
\begin{align}
   h'(t) &= Ah(t) + Bx(t) \quad \text{(1a)} \nonumber \\
   y(t) &= Ch(t) \quad \text{(1b)} \nonumber \\
   h_t &= \overline{A}h_{t-1} + \overline{B}x_t \quad \text{(2a)} \nonumber \\
   y_t &= Ch_t \quad \text{(2b)} \nonumber \\
   \overline{K} &= (C\overline{B}, C\overline{A}\overline{B}, \ldots, C\overline{A}^{k-1}\overline{B}, \ldots) \quad \text{(3a)} \nonumber \\
   y &= x * \overline{K} \quad \text{(3b)} \nonumber
\end{align}
\begin{itemize}
   \item In the first stage (1a \& 1b), the continuous parameters $h'(t)$ are transformed into discrete parameters $h_t$ through a fixed formula $\overline{A} = f_A(\Delta t, A)$ and $\overline{B} = f_B(\Delta t, A, B)$, where $(f_A, f_B)$ is called the discretization rule. The most common is the zero-order hold (ZOH) rule, defined as $\overline{A} = \exp(\Delta t A)$ and $\overline{B} = (\Delta t A)^{-1} (\exp(\Delta t A) - I) \cdot \Delta t B$.
   \item In the second stage (2a \& 2b and 3a \& 3b), after the parameters are transformed from $(\Delta t, A, B, C)$ to $(\overline{A}, \overline{B}, C)$, linear recursion or global convolution can be used for computation.
\end{itemize}
State space models cannot update states selectively based on different input information.

The solution of selective state space models (Mamba~\citep{gu2023mamba}) is that, compared to state space models that compress all historical information, they design a simple selection mechanism that parameterizes the input of the state space model,making $(\Delta t, B, C)$  a function of the input.
